---
title: "Dislikes"
author: "Klaus Frieler"
date: "16.12.2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
source("dislikes.R")
master <- setup_workspace(F)
metadata <- master %>% distinct(p_id, .keep_all = T) %>% 
  select(p_id, gender, age, job, education, age_group, degree) %>% 
  mutate(age = as.numeric(age)) %>% 
  mutate(higher_ed = education %in% c("bachelor", "master", "promotion"), 
         at_least_a_level = education %in% c("bachelor", "master", "promotion", "a-levels"), 
         other_ed = !at_least_a_level)
```

## Participants

We collected data from a total of 639 participants. After inspecting the rating behaviour for anomnalities, we excluded 12 participatns, who showed 90% of all their ratings on the extreme end of the ratings scales (low or high). After this step, 
`r nrow(metadata)` participants (`r nrow(metadata %>% filter(gender == "F"))` female, `r nrow(metadata %>% filter(gender == "M"))` male) stayed in the study, with a median age of `r median(metadata$age, na.rm = T)` (range: `r sprintf("%s-%s", min(metadata$age, na.rm = T), max(metadata$age, na.rm = T))`, IQR = `r IQR(metadata$age, na.rm = T) %>% round(1)`). The age distribution appeared to be a bimodal distribution, which is rather typical for this kind of online study. Fitting a Gaussian Mixture Model (using the MClust package for R) corroborated the visual impression of two clusters. We found one age group with  participants up to 30 years (`r (table(metadata$age_group))["<=30"]`, `r (table(metadata$age_group) %>% prop.table() %>% round(3) %>% magrittr::multiply_by(100))["<=30"]`%), and another one with participants older than 30 years (`r (table(metadata$age_group))[">30"]`,  
`r (table(metadata$age_group) %>% prop.table() %>% round(3) %>% magrittr::multiply_by(100))[">30"]`%). We will use this as a variable for some of analyses down below.

The participant were mainly highly educated, with a `r (table(metadata$higher_ed) %>% prop.table() %>% round(3) %>% magrittr::multiply_by(100))["TRUE"]`% having an university or college degree (bachelor, master, or PhD), and `r (table(metadata$at_least_a_level) %>% prop.table() %>% round(3) %>% magrittr::multiply_by(100))["TRUE"]`% having a school degree of A-levels ("Abitur"), with `r (table(metadata$job) %>% prop.table() %>% round(3) %>% magrittr::multiply_by(100))[["student"]]` of the sample being students. This rather homegeneous group, unfortunately, prohibited further analysis with respect to education.


##Preprocessing (Factor Analysis)

In order to reduce the number of variables and the complexity of the analysis, we applied an exploratiry factor analysis to the rating scales, across all types and degrees of disliking. 

## Difference between Style/Artist and Strong/Slight degrees of disliking


```{r mean_value_plot_artist, echo = FALSE}
mean_value_plot(master, weighted = F, type = "artist")
```

```{r mean_value_plot_artist_weighted, echo = FALSE}
mean_value_plot(master, weighted = T, type = "artist")
```
